--- 
title: "Cambourne Premier League 2023"
author: "CPL Committee"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
#github-repo: rstudio/bookdown-demo
description: "CPL 2023 Score book."
---

# CPL 2023 Score Board {-}

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```

```{r}
rm(list=ls())
```

```{r, libraries}
library(tidyverse)
library(kableExtra)
library(readxl)
library(DT)
```

```{r}
source('./rfuncs.R')
```

## Agreement / Consent {-#consent}


Welcome to CPL 2023 Score board ! 

This website is password protected to ensure that only authorized individuals can access its information. You have entered the password accessing this website. 

By accessing this content, you acknowledge and agree to the following:

  1. The content provided on this website is intended solely for the individuals who have been granted access through the designated password.
  
  2. You understand that sharing the password or any content from this website with unauthorized individuals is strictly prohibited.
  
  3. You agree to respect the confidentiality of the information provided on this website and not to disclose, copy, or distribute any part of it without prior written consent.
  
  4. Any actions that compromise the security or integrity of this website, including attempting to bypass the password protection, are strictly prohibited.

We emphasize the importance of maintaining the exclusivity of the content on this website. If you do not agree to these terms, please exit this website immediately.

By proceeding further, you confirm your understanding of these terms and agree to abide by them.   

Thank you for your cooperation and enjoy your CPL 2023 Score board !
